### 2018-04-10 latex/icpp18/experiments.tex

%\subsection {Effect of communication scheme}

@@

\addplot  table [x={edgefactor}, y expr=(\thisrow{collective}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp1d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp2d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cr}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cu}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};\legend{COL, CH1, CH2, CR, CN}
\end{axis}
\end{tikzpicture}
\subcaption{Communication cost for $k$=48 on 4096 procs}
\label{fig:nnzsweepcomm}
\end{subfigure}

\caption{Communication and computation costs of different partitioning strategies on Kronecker graphs on 4096 processors Rhea for $k=48$}
\label{fig:kronecker}
\end{figure}

>>>>

%\subsection {Effect of communication scheme}
\subsection {Effect of communication scheme}
In \cref{fig:nnzsweep} we provide per-iteration computation and communication timings for different partitionings and communication schemes using $4096$ processors and a $64x64$ processor grid.
\krfaun is the is the implementation of \mpifaun and is the only instance that uses collective communication.
Comparing it with the \krcun that also uses uniform partitioning but with point-to-point communication, we notice that \mpifaun always incurs significantly higher communication cost.
As the edge factor increases and matrix becomes denser, the communication cost of \mpifaun does not change as expected since it does not depend on the matrix sparsity.
The communication cost of \krcun progressively increases with the edge factor, but even with an edge factor of $64$ \mpifaun takes about more time by a factor of two.
Therefore, we conclude that even though there is a converging trend between the cost of collective and point-to-point communication, it is a rather slow convergence, and the point-to-point scheme should be the method of choice unless the matrix gets very dense.

@@

\addplot  table [x={edgefactor}, y expr=(\thisrow{collective}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp1d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cp2d}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cr}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};
\addplot  table [x={edgefactor}, y expr=(\thisrow{cu}/(\minvalue*\numiterations))] {data/nnzsweepall_k48_p4096_comm.dat};\legend{COL, CH1, CH2, CR, CN}
\end{axis}
\end{tikzpicture}
\subcaption{Communication cost for $k$=48 on 4096 procs}
\label{fig:nnzsweepcomm}
\end{subfigure}
\caption{Communication and computation costs of different partitioning strategies on Kronecker graphs on 4096 processors Rhea for $k=48$}
\label{fig:nnzsweep}
\end{figure}
